Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
edits to 2.5

Alg.~\ref{mainAlgorithm} describes how we combine program search,
recognition model training, and DSL induction.
We note the following implementation details:
(1) We interleave wake cycles with each of the sleep cycles;
(2) on the first iteration, we do \emph{not} train the recognition model on samples from
the generative model because a DSL has not yet been learned --
we instead train the network to only maximize $\mathcal{L}_{\text{AE}}$.
%% (3) Because the frontiers can grow very large,
%% we only keep around the top $10^4$ programs $p$ in each frontier $\mathcal{F}_x$
%% with the highest likelihood $\probability[x,p|\mathcal{D},\theta]$.
(3) During both DSL induction and neural net training, we calculate Eq.~\ref{AIC} and $\mathcal{L}_{\text{RM}}$
by only summing over the top $K$
programs in $\mathcal{F}_x$ as measured by $\probability[x,p|\mathcal{D},\theta]$ -- we found that $K = 2$ sufficed.
(4) For added robustness, we enumerate programs from both the generative model and the recognition model.

>>>>

Alg.~\ref{mainAlgorithm} describes how we combine program search,
recognition model training, and DSL induction.
We note the following implementation details:
(1) We perform a wake cycle before each of the sleep cycles.
(2) On the first iteration, we do \emph{not} train the recognition model on samples from
the generative model because a DSL has not yet been learned --
we instead train the network to only maximize $\mathcal{L}_{\text{AE}}$.
%% (3) Because the frontiers can grow very large,
%% we only keep around the top $10^4$ programs $p$ in each frontier $\mathcal{F}_x$
%% with the highest likelihood $\probability[x,p|\mathcal{D},\theta]$.
(3) During both DSL induction and neural net training, we calculate Eq.~\ref{AIC} and $\mathcal{L}_{\text{RM}}$
by only summing over the top $K$
programs in $\mathcal{F}_x$ as measured by $\probability[x,p|\mathcal{D},\theta]$ -- we found that $K = 2$ sufficed.
(4) For added robustness, we enumerate programs from both the generative model and the recognition model.
